---
title: "hw1.Rmd"
author: "Amina"
date: Sys.time()
output: 
  html_document:
    theme: readable
    highlight: espresso
    css: style.css
    font-family: Palatino; 
    font-size: 16;
        
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

## Introduction

A section called "Introduction" where you provide a short summary of the structure of your homework. Moreover, record a short video to introduce your group and include it in your RMarkdown document.

## Group Member

A section called "Group Members". This section should have one subsection for each group member in your team. For example, a group with three members should have three subsections. Each of these subsections (named after each group member) should include small biographies containing at least the following elements:

1. An avatar picture. Make sure to include a caption for this image. Make sure all pictures have the same size.

2. A paragraph describing your favorite hobby as well as one interesting fact about yourself (preferably true).
Your favorite quote in blockquote format. Make sure to reference your quote using BibTex.

3. A table having two columns (first column containing the classes you are following this semester; second column containing the time of these classes).

4.Add at least one emoji and one Giphy per group member.

```{r pressure, echo=FALSE}
#Amina

```

<!DOCTYPE html>
<html>
<head>
<title>HTML Table Example</title>
</head>
<body>
<table>
  <tr> 
    <td>Column 1</td>
    <td>Column 2</td>
  </tr>
  <tr> 
    <td>Column 1</td>
    <td>Column 2</td>
</tr>
</table>
</body>
</html>
```{r pressure, echo=FALSE}
#Ed
```

```{r pressure, echo=FALSE}
#J
```


## RMarkdown Syntax

In this section make sure to:
Chunk option can be really usefull however it can lead to some missleading. Indeed

```{r pressure, echo=FALSE}

```

